Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the paper.qmd file

---
title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: 'January 23, 2024'
format: pdf
editor: visual
bibliography: references.bib
prefer-html: true
toc: true
toc-depth: 3
---

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-totalsum-table
#| tbl-cap: "Total sum of victims in different age group throughout the years"

@@

# Install the necessary packages if not already installed
install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"

@@

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of reported crimes") +
  scale_fill_manual(values = c(Adult = "skyblue", Youth = "orange", Child = "pink"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

# Print the bar plot
print(bar_plot)

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-crimetype-table
#| tbl-cap: "Total number of victims counted for each crime from the year 2014 to 2022"

@@

# Print the table using kable with additional styling
kable(pivoted_table_2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

>>>>

---
title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
format: pdf
editor: visual
bibliography: references.bib
prefer-html: true
toc: true
toc-depth: 3
---

∗Code and data supporting this analysis is available at:

<https://github.com/Chay-HyunminPark/Toronto_CrimeVictims.git>[^1].

[^1]: View the repository on GitHub.

...

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-totalsum-table
#| tbl-cap: "Total Sum of Victims in Different Age Groups Throughout the Years"

@@

# Install the necessary packages if not already installed
# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"

@@

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c(Adult = "skyblue", Youth = "orange", Child = "pink"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-crimetype-table
#| tbl-cap: "Total Number of Victims Counted for Each Crime from the Year 2014 to 2022"

@@

# Print the table using kable with additional styling
kable(pivoted_table_2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))
```
